|

### 2021-08-01 dissertation/msc_dissertation_introduction.Rmd
Adjusting the scripts structure to use extractor function as wrapper
Adding comments to multiverse script

---
title: "__How analysis strategy affects analysis results__"
subtitle: "Vibration of effects due to model specifications"
author: "Sebastian Ploner, sploner1@sheffield.ac.uk, University of Sheffield"
linestretch: 1.5
output: pdf_document
bibliography: references.bib
csl: apa.csl
---

@@

# Introduction

@@

The Covid-19 pandemic has reaffirmed the need for rigorous scientific research, but the process is not straightforward. In fact, Ioannidis 2005 argued that most study findings are false positives due to flawed study designs and insufficient sample sizes.

@silberzahn2018

@@

@haessler2020

@@

>>>>

---
title: |
  | __Assessing the median effect robustness in__
  | __@silberzahn2018 through model specification__
subtitle: "How analysis strategy affects analysis results"
author: "Sebastian Ploner, sploner1@sheffield.ac.uk, University of Sheffield"
linestretch: 1.5
output: pdf_document
bibliography: references.bib
csl: apa.csl
---

@@

# Introduction
     The Covid-19 pandemic has reaffirmed the need for rigours scientific research to inform decision-making on a scientific and societal level. However, particularly the social sciences have a history of inflated positive findings (Ionanidis) leading to the reproducibility crisis [@pashler2012]. @simmons2011 demonstrated how the so-called *researcher degree of freedom* affect study results. This concept refers to the analytical choices researchers make and their induced variation in results. For instance, sample size can be highly deterministic of finding statistically significant effects. @john2012 found 70% of researchers have at least once stopped their data collection based on a preliminary analysis. P-value simulations as a function of sample size showed an increased likelihood of obtaining false-positives for small sample sizes. Specifically, a sample size of ten had a 22.1% chance of being a false positive. Adding 20 observations per condition decreased the probability to 12.7% [@simmons2011]. The authors did not insinuate any malicious intent per-se, but rather attributed the issue to an ambiguity of a "right way" to analyse data, and needing statistically significant results to publish. To prevent such bad practices the authors suggest requirements and guidelines for authors and reviewers, respectively.

@@

@@

@@

# Results

# Discussion
